ZCB Pricing

### 2018-06-24 ZCB Pricing .Rmd
Real Work

>>>>

```{r 2}
# Monte Carlo Simulation

monte_carlo <- function(alpha, beta, sigma, t, T, r, n, s){
  # s = number of sub-intervals
  # n = number of simulation trials

  dt <- T/s
  sim_path <- matrix(NA,nrow = n, ncol = 1) # matrix to store simulated path integrals
  sim_r <- NULL # vector to store rates on the path

  for (d in 1:n){
    sim_r[1] <- r
    for (j in 2:s){
      mu <- alpha/beta + exp(-beta*dt)*(sim_r[j-1] -alpha/beta)
      sd <- sqrt((sigma^2/(2*beta))*(1 -exp(-2*beta*(dt))))
      sim_r[j] <- rnorm(1,mu,sd)
    }

    int <- dt*(sum(sim_r)) # integral of path
    sim_path[d,1] <- exp(-int) # bond price of path

  }
  mean(sim_path) # empirical expectation of bond price using all paths
}

```{r 3}
# Explicit Method
```

```{r 4}
# Implicit Method
```

```{r 5}
# Crank-Nicholson Method
```

```{r 6}
# Modified Fully Implicit Method
```

```{r 7, echo = FALSE}
# Comparison of results
# Varying short rates

compare_mat <- matrix(NA,nrow = 10, ncol = 8) # matrix of comparison

colnames(compare_mat) <- c("Alpha","Beta","Sigma","Initial rate","Known Price","Monte Carlo"," MC System Time","MC Squared Deviations")

a = 0.01
b = 0.1
s = 0.04
t= 0
T = 1

for (j in 1:10){
  compare_mat[j,1] <- a
  compare_mat[j,2] <- b
  compare_mat[j,3] <- s
  compare_mat[j,4] <- 0.01 +0.01*(j-1)
  compare_mat[j,5] <- bond_price(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], t= 0, T = 1, r = compare_mat[j,4])
  start_time <- proc.time()[1]
  compare_mat[j,6] <- monte_carlo(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], t= 0, T = 1, r = compare_mat[j,4], n = 1000, s=250)
  compare_mat[j,7] <- proc.time()[1] -start_time
  compare_mat[j,8] <- (compare_mat[j,6] -compare_mat[j,5])^2
}

var <- sum(compare_mat[,8])/9

library(knitr)
kable(compare_mat,align = "c")
